\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\author{GROUP 10}
\title{THE AGRI-CONNECT MOBILE APPLICATION}

\begin{document}
\begin{Huge}
\begin{center}
\begin{normalsize}
\textbf{MAKERERE UNIVERSITY }\\
\textbf{COLLEGE OF COMPUTING AND INFORMATION SCIENCES} \\
\textbf{SCHOOL OF COMPUTING AND INFORMATICS TECHNOLOGY} \\
\textbf{DEPARTMENT OF COMPUTER SCIENCE} \\
\textbf{BACHELOR OF SCIENCE IN COMPUTER SCIENCE} \\
\textbf{BIT 2207 RESEARCH METHODOLOGY} \\
\textbf{Course Work: Assignment 5}\\
\textbf{GROUP TEN(10)}
\end{normalsize}
\end{center}
\end{Huge}

\begin{center}
\begin{tabular}{|l|l|l|c|}
\hline NAME  & REG NO & STD NO \\\hline
ALEX ALINAITWE & 16/U/81 & 216000284 \\\hline
PETER WAUYO & 16/U/1273 & 216000270 \\\hline
JOSHUA MABINGO & 15/U/7254/EVE & 215011664 \\\hline
MUHWEZI JOEL & 16/U/19699/EVE & 216021707 \\\hline
\end{tabular}

\paragraph{}
RESEARCH PROPOSAL:
\end{center}

\newpage
\maketitle


\paragraph{1.  Introduction}
\paragraph{1.1  Background}
\begin{flushleft}
The advancement of technology and information development is evident in our everyday lives. Seeing from the user end perspective, the various IT services seem simple and easy functional. However, in the background, there is complex database, data ware houses and service-based technologies that become more and more wide spread. The process of buying and selling of agriculture products has been so much dictated by the middle men who hick prices for items on the side of the buyers and press the farmers buying the items at a very low price. AGRI-CONNECT is an application that is developed to cub down this problem caused by the middle men.
\end{flushleft}


\paragraph{1.2  Statement of the Problem}
\begin{flushleft}
So long us life exists, the buying and selling of agricultural products will never cease, so in the fight to increase the amount of the product sold by the farmer and also cheapen the buying price on to the buyers, AGRI-CONNECT has been built to disconnect the middle men from this formula so that our main objective is fulfilled.
\end{flushleft}



\paragraph{1.3	Objectives}
\paragraph{1.3.1  General Objective}
\begin{flushleft}
To develop an applicative solution to link the farmers directly to the buyers without the middle men.
\end{flushleft}

\paragraph{1.3.2  Specific Objectives}
\begin{flushleft}
To enable a common farmer sale his products directly to the buyers and a relatively fair price than that suggested by the middle men.
\end{flushleft}

\begin{flushleft}
To enable buyers, purchase items from farmers at a cheaper price.
\end{flushleft}

\begin{flushleft}
To create user friendly systems.
\end{flushleft}

\paragraph{1.4  Scope}
\begin{flushleft}
The application is built for farmers and buyers of agricultural products.
\end{flushleft}

\paragraph{1.5  Significance of the Study}
\begin{flushleft}
This study is important because it eliminates the middle men from this formulae of buying and selling of agricultural products.
\end{flushleft}

\end{document}
