\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\author{De Brayo}
\begin{document}
\paragraph{1.  Introduction}
\paragraph{1.1  Background}
\begin{flushleft}
The advancement of technology and information society is evident in our everyday life. Seeing from the end user perspective, the various IT services that we use daily seem simple and easy functional. However, in the background, there are complex databases, data warehouses and service-based technologies that become more and more widespread. Databases are used to store various types of information in hospitals, schools, universities, municipalities, government agencies and almost in all businesses services. In these complex systems, the management and presentation of the information stored in the databases are strictly defined within the software applications and information systems. Only a small room for customization is left to the people who actually use the information.
\end{flushleft}

\begin{flushleft}
The document and report templates that are an essential parts of any software
application or information system are most often predefined, and the user can only
choose from the predefined templates to generate documents or reports. With this
concept, the template generating process is limited to the programmers and database
administrators. The common software user can use only the previously defined
document and report templates. In this paper we propose an applicative solution for
generating documents and reports from user defined templates - ASGRT. 
\end{flushleft}

\paragraph{1.2  Statement of the Problem}
\begin{flushleft}
There is, currently, an abundance of database usage
in almost all aspects of our lives. However, most of the end users have neither the
knowledge nor the need to manage the databases. Even more important, they are
unable to generate the ever-changing reports they need, based on the data in their
databases. 
\end{flushleft}

\begin{flushleft}
Our Simple Report Generation System(SRGS) will deal with this issue efficiently. It has a simple yet effective architectural design aimed to give power to the more experienced administrators and simplicity to common end users, to generate reports with their own criteria and design, from their databases.
\end{flushleft}

\paragraph{1.3	Objectives}
\paragraph{1.3.1  General Objective}
\begin{flushleft}
To develop an applicative solution for generating documents and reports from user defined templates.
\end{flushleft}

\paragraph{1.3.2  Specific Objectives}
\begin{flushleft}
To enable the common user to create his own templates and gather the info he needs from the database.
\end{flushleft}

\begin{flushleft}
To enable interoperability so that the system is able to work with all kinds of SQl databases.
\end{flushleft}

\begin{flushleft}
To create a user-friendly system.
\end{flushleft}

\paragraph{1.4  Scope}
\begin{flushleft}
The research is aimed at students and staff at Makerere University who have access to the university database. 
\end{flushleft}

\paragraph{1.5  Significance of the Study}
\begin{flushleft}
This study is important because it aims at simplifying report generating from the database, by various types of end users in Makerere University.
\end{flushleft}

\end{document}

